---
title: "p8105_hw6_mf3593"
author: "Miao Fu"
date: "2023-11-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
```

## Problem 1
```{r}
homicide=read.csv("homicide-data.csv",na = c("", "NA", "Unknown"))|>
  janitor::clean_names()|>
  mutate(city_state=paste0(city," , ",state),
         homicide_bin=ifelse(disposition=="Closed by arrest",1,0),
         victim_age=as.numeric(victim_age))|>
  filter(!city_state%in%c("Dallas , TX","Phoenix , AZ", "Kansas City , MO", "Tulsa , AL"),
         victim_race%in%c("White","Black"))|>
  select(city_state, homicide_bin, victim_age, victim_sex, victim_race)


homicide|>
  filter(city_state==("Baltimore , MD"))|>
  glm(homicide_bin ~ victim_age+victim_sex+victim_race,data=_,family=binomial())|>
  broom::tidy()|>
  mutate(
    OR=exp(estimate),
    OR_CI_upper = exp(estimate + 1.96 * std.error),
    OR_CI_lower = exp(estimate - 1.96 * std.error)) |> 
  filter(term == "victim_sexMale") |> 
  select(OR, OR_CI_lower, OR_CI_upper) |>
  knitr::kable(digits = 3)

homicide|>
  nest(data=-city_state)|>
  mutate(
    model = map(data,\(df) glm(homicide_bin ~ victim_age+victim_sex+victim_race,data=df,family=binomial())),
    results = map(model, broom::tidy))|>
  select(-data, -model)|> 
  unnest(results)|>
  mutate(
    OR=exp(estimate),
    OR_CI_upper = exp(estimate + 1.96 * std.error),
    OR_CI_lower = exp(estimate - 1.96 * std.error)) |> 
  filter(term == "victim_sexMale") |> 
  select(city_state, OR, OR_CI_lower, OR_CI_upper)|>
  mutate(
    city_state = fct_reorder(city_state, OR))|>
  ggplot(aes(x=city_state,y=OR))+
  geom_point()+
  geom_errorbar(aes(ymin = OR_CI_lower, ymax = OR_CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
  
```

The odds ratio are overall low (0-2) for all cities. It means male victims has a lower chance of having case closed compared to other sex in most cities. New York has the smallest odds ratio. CI are mostly narrow, suggesting the difference in resolution of case between sexes is significant. 


## Problem 2

```{r}
set.seed(1)

weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())

boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}

boot_straps = 
  tibble(strap_number = 1:5000) |> 
  mutate(
    strap_sample = map(strap_number, \(i) boot_sample(df = weather_df))
  )

log_multiple=boot_straps|>
  mutate(
    models=map(strap_sample,\(df) lm(tmax~tmin+prcp,data=df)),
    results=map(models,broom::tidy)
  )|>
  select(-strap_sample,-models)|>
  unnest(results)|>
  select(strap_number,term,estimate)|>
  filter(term %in% c("tmin","prcp"))|>
  group_by(strap_number)|>
  summarise(log_b1_b2=log(prod(estimate)))

log_multiple|>
  summarise(count=sum(is.na(log_b1_b2)),
            n=n(),
            frac=count/n())|>
  knitr::kable()
  
 
R=boot_straps|>
  mutate(
    models=map(strap_sample,\(df) lm(tmax~tmin+prcp,data=df)),
    results=map(models,broom::glance)
  )|>
  select(-strap_sample,-models)|>
  unnest(results)|>
  select(strap_number,r.squared)

combined=R|>
  full_join(log_multiple,by=strap_number)


```


## Problem 3

```{r}
child_bw=read.csv("birthweight.csv")|>
  janitor::clean_names()|>
  mutate(
    babysex=case_match(
      babysex,
      1~"male",
      2~"female"
    ),
    frace=case_match(
      frace,
      1~"White",
      2~"Black",
      3~"Asian",
      4~"Puerto Rican",
      8~"Other",
      9~"Unknown"
    ),
    malform=case_match(
      malform,
      0~"absent",
      1~"present"
    ),
    mrace=case_match(
      mrace,
      1~"White",
      2~"Black",
      3~"Asian",
      4~"Puerto Rican",
      8~"Other",
      9~"Unknown"
    )
  )|>
  na.omit(df)
```

I would propose a multiple linear regression model for birth weight.\
Hypothesis: Child birthweight is affected by babysex, gestational age in weeks, and presence of malformations that could affect weight.

```{r}
linear_mod = lm(bwt ~ babysex+gaweeks+malform, data = child_bw)
child_bw |> 
  add_predictions(linear_mod) |> 
  ggplot(aes(x = gaweeks, y = bwt,color=malform)) + 
  geom_point() +
  facet_wrap(~babysex,scale="free")+
  geom_line(aes(y = pred), color = "blue")

```

